Bird beak's elaboration and innovation

### 2022-11-09 Analysis/08-Supplementary_figures_tables.Rmd
Update 08-Supplementary_figures_tables.Rmd

## Creating the subsets
superorder_shapespace <- MCMCglmm.subsets(n = 1000, # Just run it on 1k matrices for now
      data          = shapespace,
      posteriors    = shapespace_allbirds_lvl_superorder_order,
      group         = MCMCglmm.levels(shapespace_allbirds_lvl_superorder_order)[c(super_lvl, phylo_lvl)],
      rename.groups = c(levels(shapespace$level1)[-1], "phylogeny")) #[-1] is because the first level is ""

order_shapespace <- MCMCglmm.subsets(n = 1000, # Just run it on 1k matrices for now
      data          = shapespace,
      posteriors    = shapespace_allbirds_lvl_superorder_order,
      group         = MCMCglmm.levels(shapespace_allbirds_lvl_superorder_order)[c(order_lvl, phylo_lvl)],
      rename.groups = c(levels(shapespace$level2)[-1], "phylogeny")) #[-1] is because the first level is ""
## Clean garbage
rm(shapespace_allbirds_lvl_superorder_order)

>>>>

## Creating the subsets
superorder_shapespace <- MCMCglmm.subsets(
      data          = shapespace,
      posteriors    = shapespace_allbirds_lvl_superorder_order,
      group         = MCMCglmm.levels(shapespace_allbirds_lvl_superorder_order)[c(super_lvl, phylo_lvl)],
      rename.groups = c(levels(shapespace$level1)[-1], "phylogeny")) #[-1] is because the first level is ""

order_shapespace <- MCMCglmm.subsets(
      data          = shapespace,
      posteriors    = shapespace_allbirds_lvl_superorder_order,
      group         = MCMCglmm.levels(shapespace_allbirds_lvl_superorder_order)[c(order_lvl, phylo_lvl)],
      rename.groups = c(levels(shapespace$level2)[-1], "phylogeny")) #[-1] is because the first level is ""
## Clean garbage
rm(shapespace_allbirds_lvl_superorder_order)
